---
title: "Lab 00 - Hello IDS!"
author: "Kiki Majekodunmi"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Mariam", "Kiki", 
           "member 3", "member 4"),
  github_username = c("mcgregors-garden", "mariam0306", "kiki-xox", 
                      "username 3", "username 4"), 
  colour = c("powderblue", "blue", "lightblue", 
             "colour 3", "colour 4"),
  hobby = c("Hopping", "reading", "football", 
            "football", "hobby 4"),
  favourite_number = c(2, 3, 4, NA, NA)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


A bar chart of team members github usernames against favourite number.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github_username", 
          y = "favourite_number",
          title = "Favourate numbers of each github username")
```

Good labels are critical for making your plots accessible to a wider audience. Always ensure the axis and legend labels display the full variable name. Use the plot title and subtitle to explain the main findings. It's common to use the caption to provide information about the data source. tag can be used for adding identification tags to differentiate between multiple plots.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Instead of using a bar chart use a standard graph displaying the names of the members down the first columb and their hobbies down the second columb next the the respective members.*Remove this text (including the stars) and add your answer for Exercise 20 here.*
